### 2019-11-22 3_implementation.tex
More minor edits.
edits on implemntations

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models: MPI~\cite{MPI} (with bulk
synchronous and point-to-point communication) and MPI+X (with OpenMP
and CUDA); PGAS and actor models: Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93}, X10~\cite{X1005}; and newer task-based
systems: OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40} (with task
dependencies), PaRSEC (with \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}), Realm~\cite{Realm14},
Regent~\cite{Regent15}, and StarPU~\cite{StarPU11}. Also, we consider
several systems used in large scale data analytics and workflows:
Dask~\cite{Dask15}, Spark~\cite{Spark10}, Swift/T~\cite{Wozniak13},
and TensorFlow~\cite{TensorFlow15}. We describe the systems, and any
salient details of their Task Bench implementations, below.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel actor-based programming system. Actors, or
\emph{chares}, are objects in their own address space.
Chares communicate data and synchronize via messages and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column. Messages implement dependencies; a task executes as soon as its
dependencies are all available.

@@

Dask~\cite{Dask15} is an implicitly parallel task-based programming system for large
scale data analytics with Python. Dask provides abstractions over
distributed NumPy arrays and Pandas dataframes, and also a lower-level
interface for launching tasks. We use the lower-level interface to
implement Task Bench.

@@

OmpSs~\cite{OmpSs11} and OpenMP~\cite{OpenMPSpec40} are programming
models for loop- and task-based parallelism. (OmpSs is
source-compatible with OpenMP.) The implementations use OpenMP 4.0
task dependencies.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. The implementations are otherwise straightforward.  For OpenMP,
we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

Regent~\cite{Regent15} is an implicitly-parallel task-based language
which implements the Legion programming model~\cite{Legion12}. We use
Regent rather than Legion directly because the Regent compiler
provides a critical optimization that
improves scalability~\cite{ControlReplication17}.

@@

StarPU~\cite{StarPU11} is a task-based system that supports a \emph{sequential task flow} (STF)
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC.
%% We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
%% project~\cite{Chameleon}.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of HPC workflows. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}. Our Task Bench in Swift/T is straightforward, using Swift/T's dataflow
semantics to capture dependencies on other tasks.

@@

TensorFlow~\cite{TensorFlow15} is a programming system designed for
deep learning workloads. Although TensorFlow's API exposes
machine learning concepts, internally TensorFlow is a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs operate via explicit graph construction. Task graphs are composed in Python and run by an
execution engine written in C++. Our Task Bench implementation is straightforward.

>>>>

We have implemented Task Bench in the 15 parallel and distributed
programming systems listed in Table~\ref{tab:systems}. These include
traditional HPC programming models: MPI~\cite{MPI} (with bulk
synchronous and point-to-point communication) and MPI+X (with OpenMP
and CUDA); PGAS and actor models: Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93}, X10~\cite{X1005}; and newer task-based
systems: OmpSs~\cite{OmpSs11}, OpenMP~\cite{OpenMPSpec40} (with task
dependencies), PaRSEC (with \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}), Realm~\cite{Realm14},
Regent~\cite{Regent15}, and StarPU~\cite{StarPU11}. Also, we consider
several systems used in large scale data analytics and workflows:
Dask~\cite{Dask15}, Spark~\cite{Spark10}, Swift/T~\cite{Wozniak13},
and TensorFlow~\cite{TensorFlow15}. We describe the systems and their implementations below.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel actor-based programming system. Actors(
\emph{chares}) are objects in their own address space.
Chares communicate data and synchronize via messages and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column. Messages implement dependencies; a task executes as soon as its
dependencies are all available.

@@

Dask~\cite{Dask15} is an implicitly parallel task-based programming system for large
scale data analytics with Python. Dask provides abstractions over
distributed NumPy arrays and Pandas dataframes, and also a lower-level
interface for launching tasks. We implement Task Bench in the lower-level interface.

@@

OmpSs~\cite{OmpSs11} and OpenMP~\cite{OpenMPSpec40} are programming
models for loop- and task-based parallelism. (OpenMP is
source-compatible with OmpSs.) The implementations use OpenMP 4.0
tasking.  Because tasks have a fixed number of dependencies,
we use a switch statement to implement dynamic dependencies for Task
Bench. For OpenMP, we tested GNU GOMP and Intel KMP and found KMP to be better
performing.

@@

Regent~\cite{Regent15} is an implicitly-parallel task-based language
which implements the Legion programming model~\cite{Legion12}. We use
Regent rather than Legion since the Regent compiler
provides a critical optimization to
improve scalability~\cite{ControlReplication17}.

@@

StarPU~\cite{StarPU11} is a task-based system utilizing a \emph{sequential task flow}
programming model similar to PaRSEC's DTD. Our Task Bench implementation in
StarPU is very similar to PaRSEC.
%% We use a simplified version of the 2D block cyclic data distribution from the Chameleon 
%% project~\cite{Chameleon}.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of HPC workflows. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}. 
Our Task Bench in Swift/T uses it's dataflow
semantics to capture dependencies on other tasks.

@@

TensorFlow~\cite{TensorFlow15} is a programming system designed for
deep learning workloads. Although TensorFlow's API exposes
machine learning concepts, internally TensorFlow is a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs operate via explicit graph construction. Task graphs are composed in Python and run by an
execution engine written in C++.
